Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-10 paper/main.tex
sheaves pulled to intro and shortened

This is illustrated in \autoref{fig:related-work:fiber-bundle}, wherein values lives in the fiber $\dfiber\subseteq\dtotal$. In this example, the fiber \dfiber\ is the cartesian product of two sets $F_{0}\times F_{1}$ where each fiber $F_{i}$ is ....
\begin{equation}
  formal equation of the fiber?
  \label{eq:related-work:fiber}
\end{equation}

While the values are embedded in \dfiber, the continuity of the data is modeled as the base space \dbase, which is the quotient space \cite{QuotientSpaceTopology2020}
\begin{equation}
formal math of the base space as equivalence class for F_[k]
\end{equation}
which means that every point in $\dfiber_{k}$ maps to a point $k \subset K$.

@@

@@

 The artist takes as input the sheaf object $\sheaf_{\dtotal}$ because the sheaf is a way of keeping track of how data over topological spaces is glued together \cite{ghristElementaryAppliedTopology2014}. This bookkeeping is  illustrated in \autoref{eq:artist:presheaf} as the preservation of inclusion maps $\iota, \iota^{*}$ in presheaf maps between open sets $U_i$ and their corresponding set of sections $\Gamma(U_i, \dtotal)$. A presheaf is a contravariant functor from an arbitrary category $\mathcal{C}$ to \textbf{Set} \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf} and sheafs are presheafs where sets of sections $\Gamma$ are defined over unions of open sets $U \cup_{U\in \mathscr{U}}$ \cite{spanier1989algebraic, nlab:sheaf}.

 The functor $\sheaf_{\dtotal}$ is contravariant because the inclusion map $\iota$ between open sets $U_i \in \mathcal{K}$ goes in the opposite direction from the map $\iota^*$ between the sections in $\Gamma(U_{i}, \dtotal)$ \cite{riehlCategoryTheoryContext}. The open set $U_1$ is a subset of $U_2$, therefore $\iota: U_1 \rightarrow U_2$. On the other hand, a set of functions defined on a space $U_2$ must be defined on the subspace $\iota: \Gamma(U_2, \dbase) \rightarrow \Gamma(U_1, \dbase)$ but the reverse does not need to be true. For example, a continuous function defined over the interval $\left[.25,.5\right]$ need not be defined over $\left[0, 1\right]$ but must exist over  $\left[.3, .45\right]$. We use the notation $\mathcal{K}^{op}$ to signify that the functor $\sheaf$ is contravariant and $\sheaf$ to denote that it is a sheaf. We also denote the sheaf over the total space \dbase\ of the fiber bundle \dtotal\ as $\sheaf(\dtotal)$.

>>>>

How these spaces fit together is illustrated in \autoref{fig:related-work:fiber-bundle}, wherein values lives in the fiber $\dfiber\subseteq\dtotal$. In this example, the fiber \dfiber\ is the cartesian product of two sets $F_{0}\times F_{1}$ where each fiber $F_{i}$ is ....
\begin{equation}
  formal equation of the fiber?
  \label{eq:related-work:fiber}
\end{equation}

@@

The set of all sections sections $\{\dsection^{i}: \U_{j}\rightarrow \dtotal\}|_{i\in I}$ over an arbitrary open set $U_{j}$ is denoted $\Gamma(U_{\dbasepoint}, \dtotal)$. The set of all sections over the total space \dbase\ is denoted $\Gamma(\dbase, \dtotal)$.

The map from the open set to the set of sections is called a presheaf $\sheaf: U_j \rightarrow \Gamma(U_j, \dtotal)$ \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves inclusion maps between the open sets and the sets of sections

meaning that the presheaf ensures that given an inclusion map between open sets $\iota$, there is a corresponding map $\iota^*$ between the sets of sections. This means that a smaller space $U_1$ is included in a larger space $U_2$ and a function that is continuous over a larger space $U_2$ is continuous over a subspace $U_1 \subspace U_2$. Sheaves are presheafs where sets of sections $\Gamma$ are defined over unions of open sets $U \cup_{U\in \mathscr{U}}$ \cite{spanier1989algebraic, nlab:sheaf}. Because they preserve inclusion maps, sheaves are often used as an abstraction for keeping track of how data over topological spaces is glued together \cite{ghristElementaryAppliedTopology2014}.

@@
